Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-25 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Changed those wrong where to were

As a case study, a IEA was developed using the 
EvoSpace-Interactive (ES-I) platform \cite{garcia2013evospace}. %citation
A brief description of the application is presented next, focusing
on the data elements that where ported to the graph model.

@@

\item Participation. This value is simply the degree of the user node 
in the graph. This measure also considers the number of users he knows,
perhaps some of the users where invited to the system by him.   
\end{itemize}

Three versions were compared:
\begin{itemize}
\item Base (B). All users have the same weight.
\item Non Graph Gamification (G). Only experience is considered
\item Graph Gamification (GG) . Both experience and participation are considered.
\end{itemize}
When gamification was employed, all score values known where presented to users
and a ranking of users by weight was shown in a window, a screen capture of
this interface is shown in figure \ref{fig:top-users}.

@@

\subsubsection{ Base deployment}
After a week of the anouncement the total number of volunteers for this experiment was 53 registered users. 
The total number of nodes generated in the graph was 595, with a total of 2220 relationships. In this
experiment a total of 500 new individuals where generated. The total number of evaluated
individuals for each volunteer is presented in figure \ref{fig:top-ranked-participation} with a blue line.

@@

\subsubsection{ Graph Gamification deployment}
This experiment had the higher number of volunteers for for a total of 68 registered users. 
In this experiment a total of 3594 new individuals where generated in the experiment. 
The total number of evaluated individuals for each volunteer is presented in figure 
\ref{fig:top-ranked-participation} in green.

The results presented in figure \ref{fig:top-ranked-participation}, show that those users with
higher level of participation in deployments B and G, had about the same behavior, but the difference
came with users with medium level of participation, in this case participants where more engaged in deployment
G. When comparing all the experiments the deployment GG had the higher number of participation in users
of all levels.

>>>>

As a case study, a IEA was developed using the 
EvoSpace-Interactive (ES-I) platform \cite{garcia2013evospace}. %citation
A brief description of the application is presented next, focusing
on the data elements that were ported to the graph model.

@@

\item Participation. This value is simply the degree of the user node 
in the graph. This measure also considers the number of users he knows,
perhaps some of the users were invited to the system by him.   
\end{itemize}

Three versions were compared:
\begin{itemize}
\item Base (B). All users have the same weight.
\item Non Graph Gamification (G). Only experience is considered
\item Graph Gamification (GG) . Both experience and participation are considered.
\end{itemize}
When gamification was employed, all score values known were presented to users
along with a ranking of users by their weight was shown in a window, as an example
a screen capture of this interface is shown in figure \ref{fig:top-users}.

@@

\subsubsection{ Base deployment}
After a week of the anouncement the total number of volunteers for this experiment was 53 registered users. 
The total number of nodes generated in the graph was 595, with a total of 2220 relationships. In this
experiment a total of 500 new individuals were generated. The total number of evaluated
individuals for each volunteer is presented in figure \ref{fig:top-ranked-participation} with a blue line.

@@

\subsubsection{ Graph Gamification deployment}
This experiment had the higher number of volunteers for for a total of 68 registered users. 
In this experiment a total of 3594 new individuals were generated in the experiment. 
The total number of evaluated individuals for each volunteer is presented in figure 
\ref{fig:top-ranked-participation} in green.

The results presented in figure \ref{fig:top-ranked-participation}, show that those users with
higher level of participation in deployments B and G, had about the same behavior, but the difference
came with users with medium level of participation, in this case participants were more engaged in deployment
G. When comparing all the experiments the deployment GG had the higher number of participation in users
of all levels.
